Contextual Combinatorial Cascading Bandits

### 2015-12-02 contextual combinatorial cascading bandits.tex
update proofs and use of language

\wei{We should unify terms, such as agent, user, player, etc. Also I suggest to refer to the agent as she, her.
Also for base arms, should we call them base arms, or items? their outcome as weights, or reward? It is fine to use up to two
terms interchangibly, but if so, we need to say it clearly at the first time the term is referred to.
Otherwise, we stick to one term.}
At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every basic arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding basic arm. Then the learning agent recommends a feasible solution $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user. 
\wei{Why using $\ba_{1}^t$, not $a_1^t$?}
Starting from the first item, the user checks the items one by one. The checking process stops if the user clicks on one item or has checked all items without clicking anyone. We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate whether the user has clicked on item $a$ or not at time $t$.

Assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation}
\label{eq:expectation}
\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$ where 
$$
\bO_t \leq \abs{\bA_t}, \bw_t(\ba_k^t) = \begin{cases} 0, ~~k < \bO_t \\ 1, ~~k = \bO_t \end{cases}
$$ 
\wei{The above definition of $\bO_t$ looks indirect to me. What about "For some $k=1,2,\ldots, |\bA_t|$, $\bO_t = k$
	if for all $j< k$, $\bw_t(\ba_j^t)=0$ and $\bw_t(\ba_k^t)=1$.}
or 
$$
\bO_t = \abs{\bA_t}, \bw_t(\ba_k^t) = 0, ~~ \forall\, k \leq \abs{\bA_t}.
$$
We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.

@@

The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm
	at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result.
Similarly, we could also consider the case of conjunctive objective. We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the {\it weight} of item $a$ at time $t$ satisfying equation (\ref{eq:expectation})). The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$. The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
\wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of
	$\gamma_{\bO_t}'$ and $\gamma_{k}'$. It is inconsistent with the above description, and I think the latter makes sense.}
\begin{align*}
\br_{\wedge, t} &= \begin{cases}
\gamma_{\bO_t - 1}'  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
\end{cases}\\
&=\begin{cases}
\gamma_{k - 1}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
\end{cases}
\end{align*}

@@

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Here we abuse the notation $\abs{\bA_s}$ to denote the number of elements in the list $\bA_s$. By equation (\ref{eq:expectation}), we have 
$$
\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
\{(\gamma_k X_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get a $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. The above notifications hold for both disjunctive and conjunctive objectives.

@@

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of item $a$ by
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When (\ref{eq:estimateTheta}) holds for time $t$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. Second, it recommends the output $\bA_t$ by the offline oracle with estimated weights $\bU_t$. Third, play $\bA_t$ and observes all feedback of items until first $0$ weight come out; the learning agent observes $\bO_t$ items and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote a matrix $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

Here is our main theorem.
\begin{theorem}
\label{thm:main}
Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq c f^*$ and regularization parameter $\lambda \geq C_\gamma$ for some constant $\frac{1}{2} < c < 1$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
\begin{equation}
R(T) = O(d^{3/4}\log^{3/4}(C_\gamma T)\sqrt{KT}),
\end{equation}
where
\begin{align*}
f^* &= \min_{1 \leq t \leq T} f_t^*\\
C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
\end{align*}
\end{theorem}

Suppose the reward function is disjunctive. At every time $t$, the forecaster recommends a list $\bA_t$. Then the user checks from the first item to the end. The weight $\bw_t(a)$ denote whether the user click on item $a$ or not. The user stops if she clicks on one item of $\bA_t$ or she has checked all items of $\bA_t$. If the user clicks on the first item, then the learning agent receives reward $1$. If the user clicks on the $k$-th reward of $\bA_t$, then the reward is $\gamma_k$. If the user doesn't click on any item, then the reward is $0$. Here we further assume $\gamma_2 \geq \gamma_3 \geq \ldots \geq \gamma_K$. If we define a function $f_{\vee}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS$ and $w = (w(1), \ldots, w(L))$ by
\begin{align*}
&f_{\vee} : \cS \times [0,1]^E \to [0,1]\\
&f_{\vee}(A,w) = \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
\end{align*}
Here we use notation that $\gamma_1 = 1$. Then the expected reward of $\bA_t$ is $f_{\vee}(\bA_t, \theta_*^{\top}x_t)$.

Then we have a relationship between $f$ and $f_{\vee}$
\begin{equation}
\label{eq:relation}
\begin{split}
&f_{\vee}(A, w; 1, \gamma_2, \ldots, \gamma_K) \\
&~~= 1 - f(A, 1 - w; 0, 1-\gamma_2, \ldots, 1-\gamma_K)
\end{split}
\end{equation}
If $\gamma$ is decreasing, then $1 - \gamma$ is increasing. Thus we have $1 - \gamma$ a feasible parameters for $f$. Then we could have a similar result for disjunctive case.
\begin{theorem}
Disjunctive case
\end{theorem}

@@

\begin{lemma}
\label{lem:increasing} 
Given $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A \in \prod^{\leq K}(E)$,
$$
f(A, w) \leq f(A, w').
$$
By relation (\ref{eq:ConDisRelation}), it also holds that
$$
f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
$$
\end{lemma}
\begin{proof}
It suffices to prove when $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
\begin{align*}
&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
\geq &~\gamma_{k-1} \cdot 0 = 0,
\end{align*}
then
\begin{align*}
&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
\end{align*}
\end{proof}

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq p_1, \ldots, p_m \leq 1$ and $u_1, \ldots, u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
\begin{align*}
f(A^{(m)}, w) &\leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
f_{\wedge}(A^{(m)}, w) &\leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,
\end{align*}
for any positive $\gamma_k, \gamma_k'$ with $\gamma_k' = 1 - \gamma_k$, where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$. Notice that the parameters involved in the conclusions are $\gamma_k, k \in [m]$ while the parameters used in the definition of $f_{\wedge}$ are $\gamma_k', k \in [m]$.
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $m = 1$.
\begin{align*}
&~~f(A^{(m+1)}, w)\\
&= f(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
&\leq f(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})\\
&\leq f(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k \\
&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - p_k) p_{m+1} + \gamma_{m+1} u_{m+1}\\
&= f(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
\end{align*}
\begin{align*}
&~~f_{\wedge}(A^{(m+1)}, w) \\
&= f_{\wedge}(A^{(m)}, w) -\prod_{k=1}^{m} w_k \\
&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
&= f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} \gamma_k u_k \\
&\qquad - (1 - \gamma_{m+1}') (1 - p_{m+1}) \prod_{k=1}^{m} p_k + (1 - \gamma_{m+1}') u_{m+1}\\
&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
\end{align*}
\end{proof}

\begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
Using lemma \ref{lem:increasing} and lemma \ref{lem:estimateU}, we can deduce 
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
Using lemma \ref{lem:estimateU} and lemma \ref{lem:estimateTech}, we can deduce
$$
f(\bA_t, \bU_t) \leq f(\bA_t, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Combining the above two inequalities with $f(A_t^{\ast}, \bU_t) \leq f(\bA_t, \bU_t)$, we can conclude that
$$
\Delta_{t, \bA_t} = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the disjunctive objective is similar.
\end{proof}

>>>>

\wei{We should unify terms, such as agent, user, player, etc. Also I suggest to refer to the agent as she, her.
Also for base arms, should we call them base arms, or items? their outcome as weights, or reward? It is fine to use up to two
terms interchangibly, but if so, we need to say it clearly at the first time the term is referred to.
Otherwise, we stick to one term.}
\shuai{I have unified all terms by {\em base arms}, {\em actions} and {\em the learning agent}}
At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. Then the learning agent recommends a feasible action $\bA_t=(\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t) \in \cS$ to the user. 
\wei{Why using $\ba_{1}^t$, not $a_1^t$?} \shuai{I think $a_1^t$ is a random variable because $\bA_t$ is random. Is it making sense?}
Starting from the first item, the user checks the items one by one. The checking process stops if the user clicks on one item or has checked all items without clicking anyone. We use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ as the {\em weight} of base arm $a$ at time $t$ to indicate whether the user has clicked on $a$ or not.

Assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation}
\label{eq:expectation}
\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. \wei{The above definition of $\bO_t$ looks indirect to me. What about "For some $k=1,2,\ldots, |\bA_t|$, $\bO_t = k$, if for all $j< k$, $\bw_t(\ba_j^t)=0$ and $\bw_t(\ba_k^t)=1$.} \shuai{I have modified accordingly.} For some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.

@@

The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result. Similarly, we could also consider the case of conjunctive objective. We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying equation (\ref{eq:expectation})). The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$. The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
\wei{For the following, why using $\gamma_{\bO_t - 1}'$ and $\gamma_{k - 1}'$ instead of $\gamma_{\bO_t}'$ and $\gamma_{k}'$. It is inconsistent with the above description, and I think the latter makes sense.} 
\shuai{This is an earlier version. I have modified it and all others.}
\begin{align*}
\br_{\wedge, t} &= \begin{cases}
\gamma_{\bO_t}'  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
\end{cases}\\
&=\begin{cases}
\gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
\end{cases}
\end{align*}

@@

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$. By equation (\ref{eq:expectation}), we have 
$$
\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
\{(\gamma_k X_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. The above notifications hold for both disjunctive and conjunctive objectives.

@@

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$  with confidence radius $\beta_t(\delta)$ under $\bV_t$ norm. Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When (\ref{eq:estimateTheta}) holds for time $t$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. Second, it recommends an action $\bA_t$ by the offline oracle with estimated weights $\bU_t$. Third, play $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote a matrix $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

Here is our main theorem.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \gamma_{K} \geq c f^*$ for some constant $c > 1$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \geq \frac{1}{4}f_{\wedge}^{\ast}$. Let regularization parameter satisfy $\lambda \geq C_\gamma$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, {\em ConComCascade} for both conjunctive and disjunctive objectives, satisfy
\begin{align}
&R(T) = O(\frac{d}{c-1} \log(C_\gamma T) \sqrt{KT}),\\
&R_{\wedge}(T) = O(\frac{d}{f_{\wedge}^{\ast}} \log(C_\gamma T) \sqrt{KT}).
\end{align}
where
\begin{align*}
f^* &= \min_{1 \leq t \leq T} f_t^*\\
C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
\end{align*}
\end{theorem}

@@

\begin{lemma}
\label{lem:increasing} 
Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; equivalently, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}(E)$, it holds that
$$
f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
$$
\end{lemma}
\begin{proof}
It suffices to prove when $A = (1, \ldots, m)$, where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
\begin{align*}
&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
\geq &~\gamma_{k} \cdot 0 = 0,
\end{align*}
then
\begin{align*}
&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
\end{align*}
By letting $\gamma_k = 1 - \gamma_k'$ and the relation (\ref{eq:ConDisRelation}), the increasing property of $f_{\wedge}$ is obtained directly.
\end{proof}

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq p_1, \ldots, p_m \leq 1$, $u_1, \ldots, u_m \geq 0$ and $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
\begin{align*}
&f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k u_k,\\
&f_{\wedge}(A^{(m)}, w) \leq f_{\wedge}(A^{(m)}, p) + \sum_{k=1}^{m} (1 - \gamma_k') u_k,
\end{align*}
where $A^{(m)} = (1, 2, \ldots, m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $m = 1$.
\begin{align*}
&~~f(A^{(m+1)}, w)\\
&= f(A^{(m)}, w) + \gamma_{m+1}\prod_{k=1}^m(1 - w_k) w_{m+1}\\
&\leq f(A^{(m)}, w) +  \gamma_{m+1} \prod_{k=1}^m(1 - p_k) (p_{m+1} + u_{m+1})\\
&\leq f(A^{(m)}, p) + \sum_{k=1}^m \gamma_k u_k \\
&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - p_k) p_{m+1} + \gamma_{m+1} u_{m+1}\\
&= f(A^{(m+1)}, p) + \sum_{k=1}^{m+1} \gamma_k u_k
\end{align*}
\begin{align*}
&~~f_{\wedge}(A^{(m+1)}, w) \\
&= f_{\wedge}(A^{(m)}, w) -\prod_{k=1}^{m} w_k \\
&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
&= f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, w) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
&\leq f_{\wedge}(A^{(m)}, p) +  \sum_{k=1}^{m} (1 - \gamma_k') u_k \\
&\qquad - (1 - \gamma_{m+1}') (1 - p_{m+1}) \prod_{k=1}^{m} p_k + (1 - \gamma_{m+1}') u_{m+1}\\
&\leq f_{\wedge}(A^{(m+1)}, p) + \sum_{k=1}^{m+1} (1 - \gamma_k') u_k
\end{align*}
\end{proof}

\begin{proof}[ of lemma \ref{lem:DeltaEstimate}]
By lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By lemma \ref{lem:estimateTech} and the definition of $\bU_t$ (\ref{eq:defU}),
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{t, A} = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the disjunctive case can be deduced similarly.
\end{proof}
